---
name: Zhijun
surname: Wang
position: "PhD Candidate"
address: "Food Quality and Design Group, Wageningen University & Research"
www: wur.nl/en/Persons/Zhijun-Z-Zhijun-Wang.htm
email: "zhijun0916@gmai.com"
#orcid: 0000-0002-9035-2362
researchgate: Zhijun_Wang27
Scholar: ZhijunWang
Linkedin: ZhijunWang
headcolor: 414141 # use black color
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    pandoc_args: ["--lua-filter=multiple-bibliographies.lua"] # used for creating bibliographies for multiple sections
csl: apa-cv.csl # change this if you want to use other citation styles
bibliography_published: "Published.bib" # use separate .bib files and assign each of them a unique key: bibliography_*
bibliography_underreview: "Under review.bib"
bibliography_inprep: "In prep.bib"
bibliography_presentations: "Presentations.bib"
nocite: '@*' # don't change this if you want to print out all the refs
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae);library(tibble)
```

# Research Interests

Food chemistry and Nutrition, food fraud, origin tractability, chemomentrics 

# Education

```{r}
tribble(
  ~ Degree, ~Advisor, ~ Year, ~ Institution, ~ Where,
  "Doctor of Food Science, Food Authenticity and Nutrition", "Correlation analysis of banana compositions and growing conditions","09/2017-10/2021", "Wageningen University & Research", "Wageningen, The Netherlands",
  "Master of Food Science and Engineering", "Structural modification and biological activity of polysaccharides", "09/2014-07/2017", "Nanchang University", "Nanchang, China",
  "Bachelor of Food Science and Engineering", NA, "09/2010-07/2014", "Nanchang University", "Nanchang, China",
) %>% 
  detailed_entries(what=Degree, when=Year, with=Institution, where=Where, why=Advisor)
```

# Publications

<!-- Notes: copy and paste the following block for any other bibliography sections with the same bibliography key matched that you assigned in YAML  -->
\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_published}
:::

\endgroup
<!-- Bib-printing block ends here. -->




# Selected Presentations

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_presentations}
:::

\endgroup


# Teaching Experience

## Course Assistant

```{r}
tribble(
  ~Year, ~Name, ~Duty,
  '09/2018 - 09/2020', "FQD-36306 Food Fraud and Mitigation","Student guidance in group discussion"
) %>% 
  detailed_entries(
    where = Year,
    with = Name, 
    what = Duty
  )
```


## Graduate Student supervisor

```{r}
tribble(
  ~Year, ~Name, ~Duty,
  '04/2018 - 08/2018', "Intern thesis;", " office hours; supervising student research projects",
  '09/2019 - 03/2020',"Master student thesis","office hours; supervising student research projects",
) %>% 
  detailed_entries(
    where = Year,
    with = Name, 
    what = Duty
  )
```

# Professional Service

## Reviewer

* Food Research International
* Journal of Food Engineering
* Journal of Food Science

