%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{414141}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Zhijun}{Wang}

\position{PhD Candidate}
\address{Food Quality and Design Group, Wageningen University \&
Research}

\email{\href{mailto:zhijun0916@gmai.com}{\nolinkurl{zhijun0916@gmai.com}}}
\homepage{wur.nl/en/Persons/Zhijun-Z-Zhijun-Wang.htm}
\researchgate{Zhijun\_Wang27}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}


\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------



% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {November 2020}
    {Zhijun Wang~~~·~~~Curriculum Vitae}
  {\thepage}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{research-interests}{%
\section{Research Interests}\label{research-interests}}

Food chemistry and Nutrition, food fraud, origin tractability,
chemomentrics

\hypertarget{education}{%
\section{Education}\label{education}}

\begin{cventries}
    \cventry{Doctor of Food Science, Food Authenticity and Nutrition}{Wageningen University \& Research}{Wageningen, The Netherlands}{09/2017-10/2021}{\begin{cvitems}
\item Correlation analysis of banana compositions and growing conditions
\end{cvitems}}
    \cventry{Master of Food Science and Engineering}{Nanchang University}{Nanchang, China}{09/2014-07/2017}{\begin{cvitems}
\item Structural modification and biological activity of polysaccharides
\end{cvitems}}
    \cventry{Bachelor of Food Science and Engineering}{Nanchang University}{Nanchang, China}{09/2010-07/2014}{\vspace{-4mm}}
\end{cventries}

\hypertarget{publications}{%
\section{Publications}\label{publications}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs_published}{}
\leavevmode\hypertarget{ref-wang2020linking}{}%
Wang, Z., Erasmus, S. W., Dekker, P., Guo, B., Stoorvogel, J. J., \&
Ruth, S. M. van. (2020). Linking growing conditions to stable isotope
ratios and elemental compositions of costa rican bananas (musa spp.).
\emph{Food Research International}, \emph{129}, 108882.

\leavevmode\hypertarget{ref-wang2020study}{}%
Wang, Z., Erasmus, S. W., Liu, X., \& Van Ruth, S. M. (2020). Study on
the relations between hyperspectral images of bananas (musa spp.) from
different countries, their compositional traits and growing conditions.
\emph{Sensors}, \emph{20}(20), 5793.

\leavevmode\hypertarget{ref-wang2018sulfated}{}%
Wang, Z., Xie, J., Shen, M., Nie, S., \& Xie, M. (2018). Sulfated
modification of polysaccharides: Synthesis, characterization and
bioactivities. \emph{Trends in Food Science \& Technology}, \emph{74},
147--157.

\leavevmode\hypertarget{ref-wang2017review}{}%
Wang, Z., Xie, J., Nie, S., \& Xie, M. (2017). Review on cell models to
evaluate the potential antioxidant activity of polysaccharides.
\emph{Food \& Function}, \emph{8}(3), 915--926.

\leavevmode\hypertarget{ref-wang2017sulfated}{}%
Wang, Z., Xie, J., Yang, Y., Zhang, F., Wang, S., Wu, T., Shen, M., \&
Xie, M. (2017). Sulfated cyclocarya paliurus polysaccharides markedly
attenuates inflammation and oxidative damage in
lipopolysaccharide-treated macrophage cells and mice. \emph{Scientific
Reports}, \emph{7}(1), 1--12.

\leavevmode\hypertarget{ref-wang2016carboxymethylation}{}%
Wang, Z., Xie, J., Shen, M., Tang, W., Wang, H., Nie, S., \& Xie, M.
(2016). Carboxymethylation of polysaccharide from cyclocarya paliurus
and their characterization and antioxidant properties evaluation.
\emph{Carbohydrate Polymers}, \emph{136}, 988--994.

\leavevmode\hypertarget{ref-wang2015sulfated}{}%
Wang, Z., Xie, J., Kan, L., Wang, J., Shen, M., Li, W., Nie, S., \& Xie,
M. (2015). Sulfated polysaccharides from cyclocarya paliurus reduce
h2o2-induced oxidative stress in raw264. 7 cells. \emph{International
Journal of Biological Macromolecules}, \emph{80}, 410--417.

\endgroup

\hypertarget{selected-presentations}{%
\section{Selected Presentations}\label{selected-presentations}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs_presentations}{}
\leavevmode\hypertarget{ref-wang_mind-wandering_2020}{}%
\textbf{Wang}, Z., Erasmus, S., \& Ruth, S. van. (2020, November).
\emph{The correlation analysis of banana composition and growing
condition based on stable isotope and elemental analysis}. Oral
presented at china international food safety \& quality conference 2020,
Shanghai, China.

\leavevmode\hypertarget{ref-wang_banana_2019}{}%
\textbf{Wang}, Z., Erasmus, S., Dekker, P., Guo, B., \& Ruth, S. van.
(2019, November). \emph{Banana provenance: Correlation of growing
conditions, stable isotopes and elemental compositions of costa rican
bananas}. Poster presented at the 33rd the european federation of food
science and technology (effost) international conference, Rotterdam, the
Netherlands.

\leavevmode\hypertarget{ref-wang_scan-geographical_2019}{}%
\textbf{Wang}, Z., Erasmus, S., \& Ruth, S. van. (2019, March).
\emph{Geographical features of bananas in costa rica and their stable
isotope ratios and elemental compositions}. Oral presented at the
benelux association of stable isotope scientists (basis) meeting, Texel,
the Netherlands.

\endgroup

\hypertarget{teaching-experience}{%
\section{Teaching Experience}\label{teaching-experience}}

\hypertarget{course-assistant}{%
\subsection{Course Assistant}\label{course-assistant}}

\begin{cventries}
    \cventry{Student guidance in group discussion}{FQD-36306 Food Fraud and Mitigation}{09/2018 - 09/2020}{}{\vspace{-4mm}}
\end{cventries}

\hypertarget{graduate-student-supervisor}{%
\subsection{Graduate Student
supervisor}\label{graduate-student-supervisor}}

\begin{cventries}
    \cventry{ office hours; supervising student research projects}{Intern thesis;}{04/2018 - 08/2018}{}{\vspace{-4mm}}
    \cventry{office hours; supervising student research projects}{Master student thesis}{09/2019 - 03/2020}{}{\vspace{-4mm}}
\end{cventries}

\hypertarget{professional-service}{%
\section{Professional Service}\label{professional-service}}

\hypertarget{reviewer}{%
\subsection{Reviewer}\label{reviewer}}

\begin{itemize}
\tightlist
\item
  Food Research International
\item
  Journal of Food Engineering
\item
  Journal of Food Science
\end{itemize}

\end{document}
